---
title: "Data 607 - Assignment3"
author: "Devin Teran"
date: "2/15/2020"
output: html_document
---
##Overview: This assignment using regular expressions in R.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(stringr)
```

## Introduction


## Problem 1:
1. Using the 173 majors listed in fivethirtyeight.com’s College Majors dataset [https://fivethirtyeight.com/features/the-economic-guide-to-picking-a-college-major/], provide code that identifies the majors that contain either "DATA" or "STATISTICS"
```{r get_major_data_from_Git_Hub}
git_hub_url <- 'https://raw.githubusercontent.com/fivethirtyeight/data/master/college-majors/majors-list.csv'
major_data <- read_csv(git_hub_url)
```

```{r clean_major_data}
colnames(major_data) <- c('Field_of_Degree_ID','Major','Major_Category')
head(major_data)
```

```{r identify_data_or_science_majors}
#Get list of majors from data
majors <- major_data$Major
grep(pattern = 'data|science',majors,value=TRUE,ignore.case=TRUE)
```
## Problem 2:
Write code that transforms the data below:

[1] "bell pepper"  "bilberry"     "blackberry"   "blood orange"

[5] "blueberry"    "cantaloupe"   "chili pepper" "cloudberry"  

[9] "elderberry"   "lime"         "lychee"       "mulberry"    

[13] "olive"        "salal berry"

Into a format like this:

c("bell pepper", "bilberry", "blackberry", "blood orange", "blueberry", "cantaloupe", "chili pepper", "cloudberry", "elderberry", "lime", "lychee", "mulberry", "olive", "salal berry")

```{r tranform_data_char_to_vector}
food <- '[1] "bell pepper"  "bilberry"     "blackberry"   "blood orange"

[5] "blueberry"    "cantaloupe"   "chili pepper" "cloudberry"  

[9] "elderberry"   "lime"         "lychee"       "mulberry"    

[13] "olive"        "salal berry"'
food <- str_replace_all(food,"\\d+","")
food <- str_replace_all(food,"\\n","")
food <- str_replace_all(food,"[\\[\\]]","")
food <- str_replace_all(food,"\\s+"," ")
food <- str_replace_all(food,'[\"]',"'")
food <- str_replace_all(food,"' '","','")
food <- str_sub(food,2,str_length(food))
food <- str_split(food,pattern=",")
food <- unlist(food)
food
```
## Problem 3:
#3 Describe, in words, what these expressions will match:
  
***"(.)\1\1"***  
This will return any character followed by the string \1\1.  
Examples: "a\1\1","2\1\1"  
```{r (.)\1\1}
string1 <- "a\1\1"
str_view(string1,"(.)\1\1")
string2 <- "2\1\1"
str_view(string2,"(.)\1\1")
```
  
***"(..)\1"***  
This will return any two characters following by the string \1.  
Examples "8d\1", "ee\1"
```{r (..)\1}
string1 <- "8d\1"  
str_view(string1,"(..)\1")  
string2 <- "ee\1"  
str_view(string2,"(..)\1")  
```
  
***"(.).\\1.\\1"***  
This will return any character, 
followed by any character, 
followed by the first character again, 
follow by any character, 
followed by the first character again.  
The portion of the string that will match this regex, must have the same 1st, 3rd and 5th character.  
```{r (.).\\1.\\1}
string1 <- "abaDa"  
str_view(string1,"(.).\\1.\\1")  
string2 <- "YabadabaDoo"  
str_view(string2,"(.).\\1.\\1")  
```

***"(.)(.)(.).*\\3\\2\\1"***   
The first three characters can be anything,  
followed by another character repeated n-number of times where n can be any number,   
followed by the third character, the second character, and the first character.  
```{r (.)(.)(.).*\\3\\2\\1}
string1 <- "abcddddddddddddddddcba"
str_view(string1,"(.)(.)(.).*\\3\\2\\1")
string2 <- "xyzuzyx"
str_view(string2,"(.)(.)(.).*\\3\\2\\1")
```
  
#4 Construct regular expressions to match words that:
Start and end with the same character.
```{r start-end-same}
test1 <- "deed"
str_view(test1,"^(.).+\\1$")
test2 <- "googling"
str_view(test2,"^(.).+\\1$")
```
Contain a repeated pair of letters (e.g. "church" contains "ch" repeated twice.)
```{r repeat_letters_beg_end}
test1 <- "church"
str_view(test1,"(..).+\\1")
test2 <- "sheesh"
str_view(test2,"(..).+\\1")
```
Contain one letter repeated in at least three places (e.g. "eleven" contains three "e"s.)
```{r one-letter-three-times}
test1 <- "melee"
str_view(test1,"(.)(.+?\\1?)+")
test2 <- "eleven"
str_view(test2,"(.)(.+?\\1?)+")
test3 <- "anacondas"
str_view(test3,"(.)(.+?\\1?)+")
test4 <- "telephone"
str_view(test4,"(.)(.+?\\1?)+")
test5 <- "googling"
str_view(test5,"(.)(.+?\\1?)+")

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

